---
title: "Performance Measures example"
author: "Manuel Gijón Agudo"
date: "9/10/2018"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
  html_document:
    toc: yes
    toc_depth: 2
    toc_float: yes
lang: en 
---

```{r loading-packages, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```


```{r input-data, include=TRUE}
datos <- read.csv("Data/vgsales.csv")
print(summary(datos))
```

## First exploratory analysis

First we have to do an exploration of the data in order to understand them and look for NA's and others anomalies that can leads as to an incorrect interpretation of the resoults of the analysis.

### The sales 

```{r pressure, echo=TRUE}
Global <- datos$Global_Sales
Others <- datos$Other_Sales
EEUU <- datos$NA_Sales 
Europe <- datos$EU_Sales
Japan <- datos$JP_Sales

zones <- c('Global', 'Others', 'EEUU', 'Europe', 'Japan')
zones_values <- c(Global, Others, EEUU, Europe, Japan) 
sales <- data.frame(zones, zones_values)

ggplot(sales, aes(x = zones, y = zones_values, fill=zones)) + 
  geom_boxplot(varwidth = TRUE, alpha=0.25) +
  theme(legend.position = "none") +
  scale_x_discrete(labels=zones)

# me falta añadir leyendas apropiadas
```

```{r, include=TRUE}
print(datos$Name[datos$EU_Sales == max(datos$NA_Sales)])
```

```{r, include=TRUE}
Global_truncado <- datos$Global_Sales[datos$Global_Sales < 0.3]
Others_truncado <- datos$Other_Sales[datos$Global_Sales < 0.3]
EEUU_truncado <- datos$NA_Sales[datos$Global_Sales < 0.3]
Europe_truncado <- datos$EU_Sales[datos$Global_Sales < 0.3]
Japan_truncado <- datos$JP_Sales[datos$Global_Sales < 0.3]

zones <- c('Global', 'Others', 'EEUU', 'Europe', 'Japan')
zones_values_truncado <- c(Global_truncado, Others_truncado, EEUU_truncado, Europe_truncado, Japan_truncado) 
sales <- data.frame(zones, zones_values_truncado)

ggplot(sales, aes(x = zones, y = zones_values_truncado, fill=zones)) + 
  geom_boxplot(varwidth = TRUE, alpha=0.25) +
  theme(legend.position = "none") +
  scale_x_discrete(labels=zones)

```


### Number of releases by year, understanding the tendencies

```{r, include=TRUE}


```

## Tendencies in genres

```{r, include=TRUE}


```

## Tendencies in Studios

```{r, include=TRUE}


```

## The Sony strategy

Suppose that you're Sony and it's the year bla bla bla, you have a new machine to release and you wonder...

- con qué géneros me centro
- qué estudios tendrán más éxito
- bla bla bla

```{r, include=TRUE}
plat <- datos$Platform
summary(plat) 
```

We start supposing for this exampla that we don't know when release to the market a new console, we use the data of the heats to find the appropiate moment trying to understand how people buy.



## The Nintendo strategy

We repeat the process for the Nintendo's plattforms and see what hapends


.